### 2023-02-21 Manuscript/Draft1.tex
manuscript update and percent area occ. update

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration's (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 (Azarovitz 1981; Politis et al. 2014). The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits \textbf{just listed a few uses of survey. change/add others?}.

The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling during approximately the same 2-3 week time period in each season.

@@

Stock assessment scientists use samples from the bottom trawl survey to estimate the abundance for each stock stock. There are a number of approaches to obtaining abundance estimates ranging from traditional design-based estimates such as the stratified mean to model-based estimates that range in complexity. The stratified mean calculates the geometric mean catch per tow and does not account for spatial variation in samples or allow the inclusion of environmental covariates. Model-based abundance estimates are often derived from model framewroks such as General Linear Models (GLM), General Additive Model (GAM), and General Linear Mixed Models (GLMM) that can incorporate both random and mixed effects. The Vector Autoregressive Spatio-Temporal (VAST) model is a spatial delta-generalized linear mixed model (Thorson 2019). VAST is a spatio-temporal statistical framework that models both abundance (biomass) and probability of occurrence (presence/absence). If desired, VAST also allows users to include covariate data to better inform the model. Covariates can be static (eg. habitat preferences) or dynamics (eg. temperature). We explore whether including environmental predictors can help inform models and provide better abundance estimates, which is particularly relevant as climate change progresses. The stratified mean calculations are straightforward and quick, while VAST models require numerous user inputs and take on the order of hours to complete. We compare the yearly estimated of abundance obtained from the stratified mean to estimates obtained from the Vector-Autoregressive Spatio-temporal (VAST) model.

@@

Our goal is to determine indexing approaches and settings that are robust to future environmental conditions and resulting spatial biomass patterns. An underlying assumption in all indexing methods is that individual random samples combine to accurately represent true abundance by a) containing a low enough noise level in the samples to allow for a discernible pattern and b) sampling all strata in which the population exists. These assumptions can be questioned given enough noise in the sampling process \textbf{cite?} and/or climate change causing a population to move into previously uninhabited strata. To simulate the impact of noise, we compare indexing estimates after adding noise to our samples versus those using the true sampling values. \textbf{BL: Help with correct notation for adding noise}. We simulate the effect of populations moving into new habitat by comparing indexing estimates using samples from all strata inhabited by each species on Georges bank to those that only include a subset of the full spatial domain for each species. We chose strata to exclude for each species by reviewing how spatial preferences evolved in our increasing temperature scenarios and removing strata that each species either shifted into, or away from. Tabl XXX lists all strata inhabited by each species, those that are removed from certain calculations, and the explanation of why these strata were removed.

@@

The goal of our project was to analyze how well contemporary population indexing methods can track population trends under a host of conditions, as depicted in Table COMBOS. Historically, Atlantic Cod has seen significant decline over the last XXX years while Haddock has increased in abundance in recent year {[}{[}can cite the 2022 management track assessments, see \url{https://apps-nefsc.fisheries.noaa.gov/saw/sari.php} for when the document becomes available{]}{]} \textbf{cite}. For this reason we compare indexing estimates using stratified random samples from decreasing population scenarios for Cod (see Table ???) and increasing population scenarios for Haddock (see Table ???). To provide a comprehensive analysis of population indexing methods we consider all possible scenario combinations for Yellowtail Flounder (see Table ???). The specific population trends used in our analyses can be see in Figure \ref{fig:pop-scenarios}

@@

General themes that exist in Tables X, Y and Z are that VAST estimates provide lower errors relative to those derived from the stratified mean, with VAST models that include covariate information providing the lowest overall errors. We also see individual cases where the stratified mean produced the lowest absolut error and instances where including covarites in VAST models actually increase the absolute error. When we reduce the number of strata that are included in indexing calculations to simulation species shifting into new territory, we typically see an increase in absolute error {[}{[}as expected{]}{]}, though there are some scenarios where the impact is minimal.

@@

In considering the Yellowtail Flounder results in Table XXX, we can see VAST estimates generally provide lower errors relative to those derived from the stratified mean, with models that include covariate information typically providing the lowest errors. However, there are several instances in which VAST failed to provide improved abundance estimates during the fall season without covariate information, producing the largest errors seen in the Table. These errors are corrected by including covariate information allowing for an improved VAST estimate that are significantly lower than their stratified mean counterparts.

@@

\caption{\label{tab:unnamed-chunk-1}Yellowtail error results}
\centering
\begin{tabular}[t]{l|l|l|l|l|l|l|l|l|l|l}
\hline
X & X.1 & X.2 & X.3 & X.4 & Constant.Population & X.5 & Increasing.Population & X.6 & Decreasing.Population & X.7\\
\hline
Temp & Covariate & Strata & Noise & season & Stratified Mean & VAST Estimate & Stratified Mean & VAST Estimate & Stratified Mean & VAST Estimate\\
\hline
const & no cov & all & no & spring & 0.21 & 0.11 & 0.16 & 0.13 & 0.23 & 0.08\\
\hline
const & no cov & all & yes & spring & 0.25 & 0.16 & 0.22 & 0.21 & 0.27 & 0.11\\
\hline
const & w/ cov & all & no & spring & 0.21 & 0.07 & 0.16 & 0.06 & 0.23 & 0.06\\
\hline
const & w/ cov & all & yes & spring & 0.25 & 0.08 & 0.22 & 0.07 & 0.27 & 0.07\\
\hline
const & no cov & all & no & fall & 0.32 & 0.68 & 0.34 & 0.36 & 0.41 & 0.81\\
\hline
const & no cov & all & yes & fall & 0.31 & 0.77 & 0.46 & 0.44 & 0.44 & 1.09\\
\hline
const & w/ cov & all & no & fall & 0.32 & 0.08 & 0.34 & 0.08 & 0.41 & 0.08\\
\hline
const & w/ cov & all & yes & fall & 0.31 & 0.11 & 0.46 & 0.17 & 0.44 & 0.18\\
\hline
const & no cov & reduced & no & spring & 0.27 & 0.19 & 0.2 & 0.15 & 0.25 & 0.19\\
\hline
const & no cov & reduced & yes & spring & 0.26 & 0.15 & 0.22 & 0.11 & 0.3 & 0.16\\
\hline
const & w/ cov & reduced & no & spring & 0.27 & 0.19 & 0.2 & 0.17 & 0.25 & 0.19\\
\hline
const & w/ cov & reduced & yes & spring & 0.26 & 0.14 & 0.22 & 0.13 & 0.3 & 0.16\\
\hline
const & no cov & reduced & no & fall & 0.47 & 0.25 & 0.41 & 0.11 & 0.55 & 0.24\\
\hline
const & no cov & reduced & yes & fall & 0.49 & 0.36 & 0.46 & 0.21 & 0.53 & 0.36\\
\hline
const & w/ cov & reduced & no & fall & 0.47 & 0.19 & 0.41 & 0.22 & 0.55 & 0.23\\
\hline
const & w/ cov & reduced & yes & fall & 0.49 & 0.17 & 0.46 & 0.19 & 0.53 & 0.24\\
\hline
increasing & no cov & all & no & spring & 0.28 & 0.11 & 0.32 & 0.13 & 0.22 & 0.15\\
\hline
increasing & no cov & all & yes & spring & 0.28 & 0.15 & 0.34 & 0.16 & 0.26 & 0.17\\
\hline
increasing & w/ cov & all & no & spring & 0.28 & 0.06 & 0.32 & 0.07 & 0.22 & 0.07\\
\hline
increasing & w/ cov & all & yes & spring & 0.28 & 0.12 & 0.34 & 0.1 & 0.26 & 0.1\\
\hline
increasing & no cov & all & no & fall & 0.51 & 1.26 & 0.3 & 0.66 & 0.28 & 1.06\\
\hline
increasing & no cov & all & yes & fall & 0.5 & 1.38 & 0.39 & 0.71 & 0.25 & 1.1\\
\hline
increasing & w/ cov & all & no & fall & 0.51 & 0.23 & 0.3 & 0.21 & 0.28 & 0.15\\
\hline
increasing & w/ cov & all & yes & fall & 0.5 & 0.28 & 0.3 & 0.37 & 0.25 & 0.2\\
\hline
increasing & no cov & reduced & no & spring & 0.31 & 0.17 & 0.4 & 0.33 & 0.32 & 0.14\\
\hline
increasing & no cov & reduced & yes & spring & 0.29 & 0.19 & 0.41 & 0.26 & 0.29 & 0.15\\
\hline
increasing & w/ cov & reduced & no & spring & 0.31 & 0.17 & 0.4 & 0.3 & 0.32 & 0.22\\
\hline
increasing & w/ cov & reduced & yes & spring & 0.29 & 0.15 & 0.41 & 0.25 & 0.29 & 0.21\\
\hline
increasing & no cov & reduced & no & fall & 0.64 & 0.75 & 0.7 & 0.49 & 0.54 & 0.6\\
\hline
increasing & no cov & reduced & yes & fall & 0.66 & 0.89 & 0.69 & 0.48 & 0.53 & 0.62\\
\hline
increasing & w/ cov & reduced & no & fall & 0.64 & 0.2 & 0.7 & 0.53 & 0.54 & 0.31\\
\hline
increasing & w/ cov & reduced & yes & fall & 0.66 & 0.13 & 0.69 & 0.5 & 0.53 & 0.32\\
\hline
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-1}Cod error results}
\centering
\begin{tabular}[t]{l|l|l|l|r|r|r}
\hline
Temp & Strata & Noise & season & VAST.No.Cov & VAST.w..Cov & Stratified.Mean\\
\hline
constant & all & no & spring & 0.11 & 0.12 & 0.36\\
\hline
constant & all & yes & spring & 0.12 & 0.15 & 0.35\\
\hline
constant & all & no & fall & 0.19 & 0.05 & 0.49\\
\hline
constant & all & yes & fall & 0.30 & 0.23 & 0.41\\
\hline
constant & reduced & no & spring & 0.17 & 0.24 & 0.41\\
\hline
constant & reduced & yes & spring & 0.20 & 0.23 & 0.46\\
\hline
constant & reduced & no & fall & 0.21 & 0.33 & 0.60\\
\hline
constant & reduced & yes & fall & 0.18 & 0.31 & 0.58\\
\hline
increasing & all & no & spring & 0.12 & 0.15 & 0.25\\
\hline
increasing & all & yes & spring & 0.19 & 0.19 & 0.27\\
\hline
increasing & all & no & fall & 0.76 & 0.13 & 0.45\\
\hline
increasing & all & yes & fall & 0.89 & 0.33 & 0.44\\
\hline
increasing & reduced & no & spring & 0.14 & 0.22 & 0.32\\
\hline
increasing & reduced & yes & spring & 0.15 & 0.21 & 0.29\\
\hline
increasing & reduced & no & fall & 0.60 & 0.31 & 0.54\\
\hline
increasing & reduced & yes & fall & 0.62 & 0.32 & 0.53\\
\hline
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-1}Haddock error results}
\centering
\begin{tabular}[t]{l|l|l|l|r|r|r|l|l}
\hline
Temp & Strata & Noise & season & VAST.No.Cov & VAST.w..Cov & Stratified.Mean & X & X.1\\
\hline
const & all & no & spring & 0.49 & 0.18 & 0.18 &  & \\
\hline
const & all & yes & spring & 0.73 & 0.43 & 0.21 &  & Haddock\\
\hline
const & all & no & fall & 0.28 & 0.05 & 0.26 &  & Increasing Population\\
\hline
const & all & yes & fall & 0.41 & 0.06 & 0.27 &  & \\
\hline
const & reduced & no & spring & 0.34 & 0.35 & 0.45 &  & \\
\hline
const & reduced & yes & spring & 0.30 & 0.33 & 0.46 &  & \\
\hline
const & reduced & no & fall & 0.36 & 0.48 & 0.54 &  & \\
\hline
const & reduced & yes & fall & 0.33 & 0.46 & 0.52 &  & \\
\hline
increasing & all & no & spring & 0.25 & 0.05 & 0.26 &  & \\
\hline
increasing & all & yes & spring & 0.30 & 0.06 & 0.31 &  & \\
\hline
increasing & all & no & fall & 0.89 & 0.23 & 0.40 &  & \\
\hline
increasing & all & yes & fall & 1.04 & 0.35 & 0.42 &  & \\
\hline
increasing & reduced & no & spring & 0.32 & 0.40 & 0.44 &  & \\
\hline
increasing & reduced & yes & spring & 0.38 & 0.37 & 0.37 &  & \\
\hline
increasing & reduced & no & fall & 0.44 & 0.64 & 0.72 &  & \\
\hline
increasing & reduced & yes & fall & 0.42 & 0.62 & 0.70 &  & \\
\hline
\end{tabular}
\end{table}

@@

@@

\begin{table}
\centering\begingroup\fontsize{10}{12}\selectfont

\begin{tabular}{l|l|l|l|l|l|r|r}

@@

Temp & Covariate & Strata & Noise & Season & Scenario & Stratified Mean & VAST Estimate\\
\multicolumn{1}{l}{\textbf{all}}\\

@@

\hspace{1em}\hspace{1em}constant & no cov & all & no & spring & Constant Population & 0.21 & 0.11\\

@@

\hspace{1em}\hspace{1em}constant & no cov & all & yes & spring & Constant Population & 0.25 & 0.16\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & all & no & spring & Constant Population & 0.21 & 0.07\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & all & yes & spring & Constant Population & 0.25 & 0.08\\

@@

\hspace{1em}\hspace{1em}constant & no cov & all & no & fall & Constant Population & 0.32 & 0.68\\

@@

\hspace{1em}\hspace{1em}constant & no cov & all & yes & fall & Constant Population & 0.31 & 0.77\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & all & no & fall & Constant Population & 0.32 & 0.08\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & all & yes & fall & Constant Population & 0.31 & 0.11\\

@@

\hspace{1em}\hspace{1em}constant & no cov & reduced & no & spring & Constant Population & 0.27 & 0.19\\

@@

\hspace{1em}\hspace{1em}constant & no cov & reduced & yes & spring & Constant Population & 0.26 & 0.15\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & reduced & no & spring & Constant Population & 0.27 & 0.19\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & reduced & yes & spring & Constant Population & 0.26 & 0.14\\

@@

\hspace{1em}\hspace{1em}constant & no cov & reduced & no & fall & Constant Population & 0.47 & 0.25\\

@@

\hspace{1em}\hspace{1em}constant & no cov & reduced & yes & fall & Constant Population & 0.49 & 0.36\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & reduced & no & fall & Constant Population & 0.47 & 0.19\\

@@

\hspace{1em}\hspace{1em}constant & w/ cov & reduced & yes & fall & Constant Population & 0.49 & 0.17\\

@@

\hspace{1em}\hspace{1em}increasing & no cov & all & no & spring & Constant Population & 0.28 & 0.11\\

@@

\hspace{1em}\hspace{1em}increasing & no cov & all & yes & spring & Constant Population & 0.28 & 0.15\\

@@

\multicolumn{1}{l}{\textbf{reduced}}\\

@@

\hspace{1em}\hspace{1em}increasing & no cov & all & yes & spring & Increasing Population & 0.34 & 0.16\\

@@

\endgroup{}

>>>>

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration's (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 (Azarovitz 1981; Politis et al. 2014). The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits

The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling during approximately the same 2-3 week time period in each season. {[}{[}the survey for the entire region takes \textasciitilde8 weeks to complete each season, the GB strata get covered in a similar time period each season because the survey starts in the south and moves north. But there are times when logistics, e.g., storms, Covid, cause a change in the timing of any particular stratum being sampled. This timing issue has come up in the past and we've looked at it using the dates of sampled stations within a particular stock definition. See for example GBYT\_survey\_timing\_cdf.png taken from the 2018 assessment of Georges Bank yellowtail flounder that I copied into a newly created ``miscellaneous'' folder on the Google Drive. Given all this, I suggest modifying the wording to something like ``NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season''{]}{]}

@@

Stock assessment scientists use samples from the bottom trawl survey to estimate the abundance for each stock stock. There are a number of approaches to obtaining abundance estimates ranging from traditional design-based estimates such as the stratified mean to model-based estimates that range in complexity. The stratified mean calculates the geometric mean catch per tow and does not account for spatial variation in samples or allow the inclusion of environmental covariates. Model-based abundance estimates are often derived from model framewroks {[}{[}frameworks{]}{]} such as General Linear Models (GLM), General Additive Model (GAM), and General Linear Mixed Models (GLMM) that can incorporate both random and mixed effects. The Vector Autoregressive Spatio-Temporal (VAST) model is a spatial delta-generalized linear mixed model (Thorson 2019). VAST is a spatio-temporal statistical framework that models both abundance (biomass) and probability of occurrence (presence/absence). If desired, VAST also allows users to include covariate data to better inform the model. Covariates can be static (eg. habitat preferences) or dynamics (eg. temperature). We explore whether including environmental predictors can help inform models and provide better abundance estimates, which is particularly relevant as climate change progresses. The stratified mean calculations are straightforward and quick, while VAST models require numerous user inputs and {[}{[}can?{]}{]} take on the order of hours to complete. We compare the yearly estimated of abundance obtained from the stratified mean to estimates obtained from the Vector-Autoregressive Spatio-temporal (VAST) model.

@@

Our goal is to determine indexing approaches and settings that are robust to future environmental conditions and resulting spatial biomass patterns. An underlying assumption in all indexing methods is that individual random samples combine to accurately represent true abundance by a) containing a low enough noise level in the samples to allow for a discernible pattern and b) sampling all strata in which the population exists. These assumptions can be questioned given enough noise in the sampling process \textbf{cite?} and/or climate change causing a population to move into previously uninhabited strata. To simulate the impact of noise, we compare indexing estimates after adding noise to our samples versus those using the true sampling values. \textbf{BL: Help with correct notation for adding noise}. We simulate the effect of populations moving into new habitat by comparing indexing estimates using samples from all strata inhabited by each species on Georges bank {[}{[}Bank{]}{]} to those that only include a subset of the full spatial domain for each species. We chose strata to exclude for each species by reviewing how spatial preferences evolved in our increasing temperature scenarios and removing strata that each species either shifted into, or away from. Tabl XXX {[}{[}needs to be added{]}{]} lists all strata inhabited by each species, those that are removed from certain calculations, and the explanation of why these strata were removed.

@@

The goal of our project was to analyze how well contemporary population indexing methods can track population trends under a variety of conditions, as depicted in Table \ref{tab:scenarios} Historically, Atlantic Cod has seen significant decline over the last XXX years while Haddock has increased in abundance in recent year {[}{[}can cite the 2022 management track assessments, see \url{https://apps-nefsc.fisheries.noaa.gov/saw/sari.php} for when the document becomes available{]}{]} \textbf{cite}. For this reason we compare indexing estimates using stratified random samples from decreasing population scenarios for Cod (see Table ???) and increasing population scenarios for Haddock (see Table ???). To provide a comprehensive analysis of population indexing methods we consider all possible scenario combinations for Yellowtail Flounder (see Table ???). The specific population trends used in our analyses can be see in Figure \ref{fig:pop-scenarios}

@@

General themes that exist in Tables X, Y and Z are that VAST estimates provide lower errors relative to those derived from the stratified mean, with VAST models that include covariate information providing the lowest overall errors. We also see individual cases where the stratified mean produced the lowest absolute error and instances where including covarites in VAST models actually increase the absolute error. When we reduce the number of strata that are included in indexing calculations to simulation species shifting into new territory, we typically see an increase in absolute error (as expected), though there are some scenarios where the impact is minimal.

@@

In considering the Yellowtail Flounder results in Tables \ref{tab:YTresultsallstrata} and \ref{tab:YTresultsreducedstrata}, we can see VAST estimates generally provide lower errors relative to those derived from the stratified mean, with models that include covariate information typically providing the lowest errors. However, there are several instances in which VAST failed to provide improved abundance estimates during the fall season without covariate information, producing the largest errors seen in the Table. These errors are corrected by including covariate information allowing for an improved VAST estimate that are significantly lower than their stratified mean counterparts.

Notes on differences between VAST settings: For YTF, 29/96 \textasciitilde{} 30\% of VAST runs with new settings were better (70\% were worse). 80/96 \textasciitilde{} 83\% of scenarios had a VAST run with a better error than the stratified mean. 15/16 of the times the stratified mean was better VAST was not using covariates. The 1 time that VAST was using covariates and was still worse than the stratified mean was IncPop\_IncTemp\_Allstrata\_WCov\_WNoise in the Fall (VAST had strong overestimate in the fall during IncPOP\_IncTemP\_allstrata for Had and YT). The overestimate in the fall only seems to be related to the way the population shifts between season. Looking at the percent shift plots, the population is shifting out of strata 16 in both seasons (large east strata). In the spring the population is shifting mostly into strata 17 (thin strata adjacent to 16), but in the fall they are shifting into both 17 and 18 (18 thin one adjacent to 17). Thus it seems like with much of the population concentrated in the really small outer most strata, VAST produces an underestimate, even with covariates

For Haddock (IncPop), 18/32 \textasciitilde{} 57\% of VAST runs better with new settings. 24/32 = 75\% of scenarios had a VAST run with a better error than the stratified mean. 14/16 VAST were better with covariates (the two that were worse were essentially the same) while only 10/16 were better without covariates. Stratified mean tended to perform better when all strata were included in the calculation, while VAST tended to perform better when strata are removed.

For Cod (DecPop), only 11/32 \textasciitilde{} 34\% of VAST runs were better with new settings. 28/32\textasciitilde{} 88\% of scenarios had a VAST run with a better estimate than the stratified mean. All 16/16 = 100\% of VAST runs with a covariate were better than the stratified mean. 12/16 VAST were better without covariates. The 4 runs without covariates that were worse were all extremely large errors and all from increasing temp in the fall (with and without all strata and noise). In the fall the population is moving out of strata 16 (large eastern strata) and 21 (north large) and into a number of strata (22 (tiny north), 24 (large north), 18 (tiny north)). Might be having trouble tracking in to smaller strata again.

@@

@@

Estimation methods that have large, inaccurate swings (stratified mean) can lead to changes in quotas that do not correspond to the true population trend, which could have a compounding effect (can lead to quotas that are too high/low given an incorrect assumption of increase/decrease in biomass). Our model has a constant assumed mortality that accounts for fishing and natural death and will not account for impacts of these decisions. VAST may provide more consistent biomass predictions(?)

@@

\caption{\label{tab:YTresultsallstrata}Yellowtail flounder error results with all strata included in calculations. Row colors correspond to the same settings applied in different seasons.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{l|l|l|l|c|c|c}

@@

\textbf{Temperature Scenario} & \textbf{Season} & \textbf{Covariate} & \textbf{Noise} & \textbf{VAST A} & \textbf{VAST B} & \textbf{Stratified Mean}\\

@@

\cellcolor{black}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor{black}{\textcolor{white}{\textbf{spring}}} & \cellcolor{black}{\textcolor{white}{\textbf{no cov}}} & \cellcolor{black}{\textcolor{white}{\textbf{no}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.13}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.11}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.21}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.14}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.16}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.25}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.07}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.21}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.25}}}\\

@@

\cellcolor{black}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor{black}{\textcolor{white}{\textbf{fall}}} & \cellcolor{black}{\textcolor{white}{\textbf{no cov}}} & \cellcolor{black}{\textcolor{white}{\textbf{no}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.63}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.68}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.32}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.80}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.77}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.31}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.14}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.08}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.32}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.17}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.11}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.31}}}\\

@@

\cellcolor{black}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor{black}{\textcolor{white}{\textbf{spring}}} & \cellcolor{black}{\textcolor{white}{\textbf{no cov}}} & \cellcolor{black}{\textcolor{white}{\textbf{no}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.14}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.11}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.18}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.15}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.05}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.06}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{spring}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.10}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.12}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.28}}}\\

@@

\cellcolor{black}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor{black}{\textcolor{white}{\textbf{fall}}} & \cellcolor{black}{\textcolor{white}{\textbf{no cov}}} & \cellcolor{black}{\textcolor{white}{\textbf{no}}} & \cellcolor{black}{\textcolor{white}{\textbf{1.46}}} & \cellcolor{black}{\textcolor{white}{\textbf{1.26}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.51}}}\\

@@

\cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{no cov}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.40}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{1.38}}} & \cellcolor[HTML]{5C5E60}{\textcolor{white}{\textbf{0.50}}}\\

@@

\cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{no}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.21}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.23}}} & \cellcolor[HTML]{A4A4A4}{\textcolor{white}{\textbf{0.51}}}\\

@@

\cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{\hspace{1em}Increasing}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{fall}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{w/ cov}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{yes}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.30}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.28}}} & \cellcolor[HTML]{D2D2D2}{\textcolor{white}{\textbf{0.50}}}\\

@@

@@

\cellcolor{black}{\textcolor{white}{\textbf{\hspace{1em}Constant}}} & \cellcolor{black}{\textcolor{white}{\textbf{spring}}} & \cellcolor{black}{\textcolor{white}{\textbf{no cov}}} & \cellcolor{black}{\textcolor{white}{\textbf{no}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.11}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.08}}} & \cellcolor{black}{\textcolor{white}{\textbf{0.23}}}\\

@@

\caption{\label{tab:YTresultsreducedstrata}Yellowtail flounder error results with certain strata excluded from calculations. Row colors correspond to the same settings applied in different seasons.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{l|l|l|l|c|c|c}

@@

@@
